\plaintitle

### 2016-04-22 paper/paper.tex

@@

\section{Visualization}\label{sec:visualization}
The visualization consists of three parts:
\paragraph{The bubble view} 
A compact view on the play-offs per season.
\paragraph{The statistics (zoom) view} 
A more detailed view on a statistic of a selected 
team.
\paragraph{The team view} 
A detailed view on how good or bad a team scores on a specific 
field position. \\
\newline
All three are discussed in more detail below. The three views are available to
the user on a single webpage. The user start on the bubble view and is able to
navigate to the statistics and team views by scrolling down or clicking on
teams.
%The webpage is built in such a way that it gives a hint to the user at the bottom
%or the top of a page when another view is available. By showing a different 
%background color and an arrow, we invite the visitor to explore other views. The 
%user is also at liberty to scroll through these views. However, a fixed scroll is
%implemeted so users will only end in complete views when moving around. Note that 
%the user also will be guided through all 3 views when performing actions described 
%in the section below.

@@

\subsection{The statistics view}
The statistics view gives a user a clear overview of how a statistic has been 
influenced compared to the year before. The view consists of 3 parts:
\paragraph{Context section} 
The top part informs the user about the shown context.
\paragraph{Arrow section} 
This section illustrates why a statistic changed.
\paragraph{Small multiples section} 
Small multiples of team statistics and how they evolve over time.
\subsubsection{Context section}
The context section should inform the user at all times of the current selections 
that have been made. The statistics view will always be based on a specific team
and season that have been selected or that are initated. This should be clear based
on the textual information in the top left. Next to that, in the top right a small 
bubble view is shown. It indicates the team selected and how well it performed in 
the play-offs during that season, as ecplained in the bubble view section. When changing teams and/or season, this view gets 
updated as well as the textual information.

\subsubsection{Arrow section of selected statistic}
This section illustrates a change for a chosen statistic for the selected team compared with the season before. This should give a visitor more insight into why a statistic changed over time. The selected team is represented by a circle in the same way as explained in the bubble view. The change for a statistic is represented by three arrows:
\begin{itemize}
    \item arrow on the left pointing towards the circle: indicating the influence of players who joined the team (team member current season, not previous season)
    \item arrow on the right of the circle: indicating how the team inherent changed (team member this season and previous season)
    \item arrow on the left pointing away from the circle: indicating the influence of players who left the team (team member previous season, not current season)
\end{itemize}
<figure of the statistics view>
The shirts next to the arrows are the shirts of players that had the biggest 
contribution to that arrow. Note that these shirts don't change in size. The box on 
the right enables the user to change between 
statistics. Next to that it informs the user of which statistic has been chosen. When 
the user hits the circle in the middle representing the teams, he is guided 
to the team view. This view will be explained in more detail in the next section.

@@

\section{Lessons learned}\label{sec:discussion}

We've learned a couple of lessons during the creation of this visualization: 
\begin{itemize}
    \item find a use case as soon as possible to built your visualization around
    \item each separate component should be a sufficient informative visualization on itself
    \item creating a custom visualization costs time and opportunities 
\end{itemize}

In what follows we will discuss our experience in more detail.

>>>>

\pagenumbering{arabic}

@@

\section{Visualization}\label{sec:visualization}
The visualization consists of three parts:
\begin{itemize}
    \item The bubble view: a compact view on the play-offs per season
    \item The statistics (zoom) view: a more detailed view on a statistic of a selected team
    \item The team view: a detailed view on how good or bad a team scores on a specific field position
\end{itemize}
All three are discussed in more detail below. The three views are available to
the user on a single webpage. The user start on the bubble view and is able to
navigate to the statistics and team views by scrolling down or clicking on
teams.
%The webpage is built in such a way that it gives a hint to the user at the bottom
%or the top of a page when another view is available. By showing a different 
%background color and an arrow, we invite the visitor to explore other views. The 
%user is also at liberty to scroll through these views. However, a fixed scroll is
%implemeted so users will only end in complete views when moving around. Note that 
%the user also will be guided through all 3 views when performing actions described 
%in the section below.

@@

\subsection{The statistics view}
The statistics view gives a user a clear overview of how a statistic has been influenced compared to the year before. The view consists of 3 parts:
\begin{itemize}
    \item Context section: the top part should inform the user of his/her
        context
    \item Arrow section: hhis section illustrates why a statistic changed
    \item Small multiples section: hmall multiples of team statistics and how they evolve over time
\end{itemize}

\subsubsection{Context section}
The context section should inform the user at all times of the current selections 
that have been made. The statistics view will always be based on a specific team
and season that have been selected or that are initated. This should be clear based
on the textual information in the top left. Next to that, in the top right a small 
bubble view is shown. It indicates the team selected and how well it performed in 
the play-offs during that season, as ecplained in the bubble view section. When changing teams and/or season, this view gets 
updated as well as the textual information.

\subsubsection{Arrow section of selected statistic}
This section illustrates a change for a chosen statistic for the selected team compared with the season before. This should give a visitor more insight into why a statistic changed over time. The selected team is represented by a circle in the same way as explained in the bubble view. The change for a statistic is represented by three arrows:
\begin{itemize}
    \item Arrow on the left pointing towards the circle: indicating the influence of players who joined the team (team member current season, not previous season)
    \item Arrow on the right of the circle: indicating how the team inherent changed (team member this season and previous season)
    \item Arrow on the left pointing away from the circle: indicating the influence of players who left the team (team member previous season, not current season)
\end{itemize}
<figure of the statistics view>
The shirts next to the arrows are the shirts of players that had the biggest 
contribution to that arrow. Note that these shirts don't change in size. The box on 
the right enables the user to change between 
statistics. Next to that it informs the user of which statistic has been chosen. When 
the user hits the circle in the middle representing the teams, he is guided 
to the team view. This view will be explained in more detail in the next section.

@@

\section{Lessons learned}\label{sec:discussion}
We've learned a couple of lessons during the creation of this visualization:
\begin{itemize}
    \item Find a use case as soon as possible to build your visualization around
    \item Each separate component should be a sufficient informative visualization on itself
    \item Creating a custom visualization costs time and opportunities
\end{itemize}
In what follows we will discuss our experience in more detail.
